---
title: "fun-programming-proj"
author: "Cianna Bedford-Petersen & Andrew Fridman"
date: "5/27/2019"
output:
  html_document
---

```{r Setup}
#Set options
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      error = TRUE,
                      fig.align = "center")

#Load libraries
#install.packages("pacman") # ASH: to properly knit the file I think this has to be commented out?
pacman::p_load(colorblindr, glue, prettyR, rio, tidyverse, viridis) # ASH: I have never seen this function before--very nice

#Import data
data <- import("./Wave1.rda")

#ASH: Just an FYI that your directory contains two project files; I'd delete one, because (while it matters less if they're in the exact same folder) it can screw up working directory issues if you have a project within a project.

```

```{r Custom Function 1 and map_df}

#What are the most popular breakfast items for 7th-12th Graders?

#Create a count of breakfast items

#Select only necessary variables and rename
bfast <- data %>% 
         select(H1GH23A, H1GH23B, H1GH23C, H1GH23D, H1GH23E, 
                H1GH23F, H1GH23G, H1GH23H, H1GH23I, H1GH23J) %>% # ASH: I modifed styling here; line of code was pretty long
         rename("milk" = H1GH23A,
                "coffee or tea" = H1GH23B,
                "cereal" = H1GH23C,
                "fruit, juice" = H1GH23D,
                "eggs" = H1GH23E,
                "meat" = H1GH23F,
                "snack foods" = H1GH23G,
                "bread, toast, or rolls" = H1GH23H,
                "other items" = H1GH23I,
                "nothing" = H1GH23J)

#custom fucntion to count number that marked yes for a given breakfast food column
count_1 <- function(x) {
           sum(x == '(1) (1) Marked', na.rm=TRUE)
}

#apply to all columns
bfast_count <- map_df(bfast, ~count_1(.x))

#table of responses
bfast_count %>% 
            gather(Food, Count) %>% 
            arrange(desc(Count)) %>% 
            knitr::kable()

#visualize with bar chart
bfast_count %>% 
            gather(food, count) %>% 
            ggplot(aes(reorder(food, count), count)) +
            geom_bar(aes(fill = food), stat="identity") + 
            coord_flip() +
            scale_fill_viridis_d(option="magma") + # ASH: I'm happy you are using the viridis palettes.. they are my fav :)
            theme_minimal() +
            labs(title = "Common Breakfast Food Choices",
                 subtitle = "For 7th-12th Graders",
                 caption = "Data Collected 1994-1995",
                 x = "",
                 y = "Count") +
            theme (legend.position = "none")
```

```{r Custom Function 2, Paralell Iteration, and Nest Mutate}

#What is the average screen time by grade iterated across race?

#Select variables and rename
screen <- data %>% 
          select(H1GI20, H1GI6A, H1GI6B, H1GI6C, H1GI6D, 
                 H1GI6E, H1GI8, H1DA8, H1DA9, H1DA10) %>% 
          rename("Grade" = H1GI20, 
                 "White" = H1GI6A,
                 "Black or African American" = H1GI6B,
                 "American Indian or Native American" = H1GI6C,
                 "Asian or Pacific Islander" = H1GI6D,
                 "Other" = H1GI6E,
                 "dominant_category" = H1GI8,
                 "television" = H1DA8,
                 "videos" = H1DA9,
                 "games" = H1DA10)

#Custom function to turn all variables numeric
numeric_col <- function(n) {
               lbls <- sort(levels(n))
               lbls <- (sub("^\\([0-9]+\\) +(.+$)", "\\1", lbls))
               n <- as.numeric(sub("^\\(0*([0-9]+)\\).+$", "\\1", n))
               n <- add.value.labels(n, lbls)
}

#apply to all colummns
screen_2 <- map_df(screen, ~numeric_col(.x))

#Wrangle race to be a useable variable
#Currently participants mark yes or no to a series of racial categories, if they mark yes for multiple racial groups then they are asked as a separate question which race they most identify with 
#We want one cohesive column that identifies either the only racial category a participant marked or if they marked multiple we want to know which race they most identify with


#Add a column that sums the number of race categories that each participant selected
screen_3 <- screen_2 %>% 
            mutate(identity = select(., White:Other) %>% 
                   rowSums(na.rm = TRUE))

#Filter for participants who only marked 1 race category
#Gather data and filter for the 1 race category that each participant chose
screen_4 <- screen_3 %>% 
            filter(identity == 1) %>% 
            gather(race, value, 
                   White, 
                   `Black or African American`, 
                   `American Indian or Native American`, 
                   `Asian or Pacific Islander`, 
                   Other) %>% 
            filter(value == 1)
  
#For those who identify with at least 2 race categories use the column indicating which race they identify with most
#Convert the dominant race column to a categorical column titled race
screen_5 <- screen_3 %>% 
            filter(identity >=2) %>% 
            rename(race = dominant_category) %>% 
            mutate(race = dplyr::recode(race, 
                   `1` = "White", 
                   `2` = "Black or African American" ,
                   `3` = "American Indian or Native American", 
                   `4` = "Asian or Pacific Islander", 
                   `5` = "Other"))
  
#Create one data frame that combines those who identifiy with 1 race category and those who identify with at least 2 race categories 
screen_6 <- left_join(screen_4, screen_5)

#Add column for weekly screen time by adding together tv, video, and videogame time
screen_7 <-  screen_6 %>% 
             mutate(screen_time = select(., television:games) %>% 
             rowSums(na.rm = TRUE)) %>% 
             mutate(Grade = factor(Grade)) %>% 
             drop_na(c("Grade", "race"))

#Create plot for white participants
screen_7 %>% 
         group_by(Grade, race) %>% 
         summarize(mean_screen = mean(screen_time)) %>%
         filter(race == "White") %>% 
         ggplot(aes(reorder(Grade, desc(Grade)), mean_screen)) +
         geom_col(aes(fill = Grade)) + 
         coord_flip() +
         scale_fill_viridis_d() +
         theme_minimal() +
         labs(title = "Average Weekly Screen Time",
              subtitle = "For White Students",
              caption = "Data Collected 1994-1995",
              x = "Grade",
              y = "Average Weekly Screen Time (in minutes)") +
         theme (legend.position = "none")

#Iterate through all racial identity options
p <- screen_7 %>% 
     group_by(Grade, race) %>% 
     summarize(mean_screen = mean(screen_time)) %>%
     ungroup() %>% 
     group_by(race) %>% 
     nest() %>% 
     mutate(plot = map2(data, race, ~
     ggplot(.x, aes(reorder(Grade, desc(Grade)), mean_screen)) +
     geom_col(aes(fill = Grade)) + 
     coord_flip() +
     scale_fill_viridis_d() +
     theme_minimal() +
     labs(title = "Average Weekly Screen Time",
          subtitle = glue("For {.y} Students"),
          caption = "Data Collected 1994-1995",
          x = "Grade",
          y = "Average Weekly Screen Time (in minutes)") +
     theme(legend.position = "none",
           plot.title = element_text(size = 8),
           plot.subtitle = element_text(size = 7),
           plot.caption = element_text(size = 5),
           axis.title = element_text(size = 6))))

#Defining plots
p1 <- p$plot[[1]]
p2 <- p$plot[[2]]
p3 <- p$plot[[3]]
p4 <- p$plot[[4]]
p5 <- p$plot[[5]]

#Plot grid
require(cowplot)
theme_set(theme_cowplot(font_size = 12))
plot_grid(p1, p2, p3, p4, p5, labels = c("A", "B", "C", "D", "E"))

# ASH: I have a feeling that, if not for the project requirements, you'd be facetting by race instead of using cowplot. 
# ASH: In the final plot, is there a way to reduce the amount of repeated text (e.g., plot caption, plot title, axis labels)?
```

```{r map2}

#Do insomnia symptoms predict depressed mood across adolescence?

#Tidy data to include only relevant variables
sleep_raw <- data %>%
             select(H1GI20, S60J, H1GH51, H1FS6) %>%
             rename(Grade = "H1GI20",
                    Insomnia = "S60J",
                    Sleep_Hours = "H1GH51",
                    Depression = "H1FS6") %>% 
             mutate(Grade = as.factor(Grade)) %>% 
             filter(Grade != "NA" &
                    Insomnia != "NA" &
                    Sleep_Hours != "NA")
    
#Clean labels
sleep_tidy <- map_df(sleep_raw, ~numeric_col(.x)) %>% 
              mutate(Grade = dplyr::recode(Grade, 
                     `7` = "Grade 7", 
                     `8` = "Grade 8" ,
                     `9` = "Grade 9", 
                     `10` = "Grade 10", 
                     `11` = "Grade 11",
                     `12` = "Grade 12"))

#Split data by grade
by_grade <- sleep_tidy %>%
            nest(-Grade)

#Model comparison (total number of sleep hours as a covariate and moderator)
sleep_models <- by_grade %>%
                mutate(m1 = map(data, 
                                ~lm(Depression ~ Insomnia, data = .x)),
                       m2 = map(data, 
                                ~lm(Depression ~ Insomnia + Sleep_Hours, 
                                    data = .x)), 
                       comp12 = map2(m1, m2, anova),
                       p12 = map_dbl(comp12, list("Pr(>F)", 2))) #ASH: This is great

#Extracing the r^2 values by model across grade
sleep_models2 <- sleep_models %>% 
                 gather(model, output, m1:m2) %>%
                 mutate(r2 = map_dbl(output, ~summary(.x)$r.squared))

#Plotting the r^2 values by model across grade
sleep_models2 %>% 
              mutate(fct_relevel(Grade, 
                                   "Grade 7", 
                                   "Grade 8", 
                                   "Grade 9", 
                                   "Grade 10",  
                                   "Grade 11", 
                                   "Grade 12")) %>% 
              ggplot(aes(model, r2)) +
                  geom_col(aes(fill = model)) +
                  facet_wrap(~Grade) +
                  scale_fill_OkabeIto() +
                  labs(title = "Insomnia (Model 1) vs. Insomnia and Total Sleep Time (Model 2) Predicting Depression",
                       caption = "Data Collected 1994-1995",
                       x = "Model",
                       y = "R^2") +
                  guides(fill = "none") +
                  theme_bw() +
                  theme(legend.position = "none",
                        plot.title = element_text(size = 10, face = "bold"))

# ASH: Here I'd recommend trying to incorporate some means of visualizing uncertainty (e.g., add error bars or star which model comparisons are significant)  
# ASH: Also, there are a lot of bar graphs (Cam and I are also guilty of this).  If you intend to create some tutorial or something similar, maybe try to mix up the visualizations?
  
```

### Ashley's peer review breakdown:

**Three areas of strength:**

  + Excellent use of commentary; Seriously by far the best I've encountered thus far. I knew what you were trying to achieve with each line of code! 
  + Great graphical presentation:
      + Good use of color-blind friendly palette
      + Each graph is clear/it doesn't take too much effort to understand the point of each graph
  + The code itself is efficient and relatively advanced. For instance, I was super impressed with your numeric_col function. Pattern matching/replacement is extremely difficult!! It's obvious you both have mastered the tidyverse, as well.  
  
**At least one thing I learned:**

  + Using `pacman::p_load` to load libraries was new to me. I'm totally going to use this in the future.
  
**Project Requirements**

  + Complete:
      + You definitely meet the requirement for using at least 2 variants of map 
      + You also created more than 2 custom functions--well done!
      + You incorporated at least one instance of parallel iteration (e.g., map2)
      + You used at least one case of purr::nest %>% mutate() 
  + Still Needed:
      + I'm unsure if this is still a requirement, but I don't think you use a function outside the basic map family (walk, reduce, modify)?
      + I assume you are using the code to either (1) build toward a cumulative product (e.g., a data product for a client, a research article, or similar) or (2) create a tutorial on functional programming and writing functions in R... but this isn't entirely clear. 
