---
title: "Final Project Presentation"
author: "Cianna Bedford-Petersen & Andrew Fridman"
date: "5/27/2019"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include = FALSE}
#Set options
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      error = TRUE
                      )

#Load libraries
pacman::p_load(colorblindr, flexdashboard, here, glue, prettyR, rio, tidyverse, viridis)

#Import data
data <- import(here("data", "Wave1.rda"))

#####Visualization 1#####

#Select only necessary variables and rename
bfast <- data %>% 
         select(H1GH23A, H1GH23B, H1GH23C, H1GH23D, H1GH23E, H1GH23F, H1GH23G, H1GH23H, H1GH23I, H1GH23J) %>% 
         rename("milk" = H1GH23A,
                "coffee or tea" = H1GH23B,
                "cereal" = H1GH23C,
                "fruit, juice" = H1GH23D,
                "eggs" = H1GH23E,
                "meat" = H1GH23F,
                "snack foods" = H1GH23G,
                "bread, toast, or rolls" = H1GH23H,
                "other items" = H1GH23I,
                "nothing" = H1GH23J
                )

#custom fucntion to count number that marked yes for a given breakfast food column
count_1 <- function(x) {
           sum(x == '(1) (1) Marked', na.rm=TRUE)
}

#apply to all columns
bfast_count <- map_df(bfast, ~count_1(.x))

#####Visualization 2#####

#Select variables and rename
screen <- data %>% 
          select(H1GI20, H1GI6A, H1GI6B, H1GI6C, H1GI6D, H1GI6E, H1GI8, H1DA8, H1DA9, H1DA10) %>% 
          rename("Grade" = H1GI20, 
                 "White" = H1GI6A,
                 "Black or African American" = H1GI6B,
                 "American Indian or Native American" = H1GI6C,
                 "Asian or Pacific Islander" = H1GI6D,
                 "Other" = H1GI6E,
                 "dominant_category" = H1GI8,
                 "television" = H1DA8,
                 "videos" = H1DA9,
                 "games" = H1DA10
                 )

#Custom function to turn all variables numeric
numeric_col <- function(n) {
               lbls <- sort(levels(n))
               lbls <- (sub("^\\([0-9]+\\) +(.+$)", "\\1", lbls))
               n <- as.numeric(sub("^\\(0*([0-9]+)\\).+$", "\\1", n))
               n <- add.value.labels(n, lbls)
}

#apply to all colummns
screen_2 <- map_df(screen, ~numeric_col(.x))

#Add a column that sums the number of race categories that each participant selected
screen_3 <- screen_2 %>% 
            mutate(identity = select(., White:Other) %>% 
                   rowSums(na.rm = TRUE))


#Filter for participants who only marked 1 race category
#Gather data and filter for the 1 race category that each participant chose
screen_4 <- screen_3 %>% 
            filter(identity == 1) %>% 
            gather(race, value, 
                   White, 
                   `Black or African American`, 
                   `American Indian or Native American`, 
                   `Asian or Pacific Islander`, 
                   Other) %>% 
            filter(value == 1)
  
#For those who identify with at least 2 race categories use the column indicating which race they identify with most
#Convert the dominant race column to a categorical column titled race
screen_5 <- screen_3 %>% 
            filter(identity >=2) %>% 
            rename(race = dominant_category) %>% 
            mutate(race = dplyr::recode(race, 
                   `1` = "White", 
                   `2` = "Black or African American" ,
                   `3` = "American Indian or Native American", 
                   `4` = "Asian or Pacific Islander", 
                   `5` = "Other"))
  

#Create one data frame that combines those who identifiy with 1 race category and those who identify with at least 2 race categories 
screen_6 <- left_join(screen_4, screen_5)

#Add column for weekly screen time by adding together tv, video, and videogame time
screen_7 <-  screen_6 %>% 
             mutate(screen_time = select(., television:games) %>% 
             rowSums(na.rm = TRUE)) %>% 
             mutate(Grade = factor(Grade)) %>% 
             drop_na(c("Grade", "race"))

#####Visualization 3#####

#Tidy data to include only relevant variables
sleep_raw <- data %>%
             select(H1GI20, S60J, H1GH51, H1FS6) %>%
             rename(Grade = "H1GI20",
                    Insomnia = "S60J",
                    Sleep_Hours = "H1GH51",
                    Depression = "H1FS6") %>% 
             mutate(Grade = as.factor(Grade)) %>% 
             filter(Grade != "NA" &
                    Insomnia != "NA" &
                    Sleep_Hours != "NA")
    
#Clean labels
sleep_tidy <- map_df(sleep_raw, ~numeric_col(.x)) %>% 
              mutate(Grade = dplyr::recode(Grade, 
                     `7` = "Grade 7", 
                     `8` = "Grade 8" ,
                     `9` = "Grade 9", 
                     `10` = "Grade 10", 
                     `11` = "Grade 11",
                     `12` = "Grade 12"))

#Split data by grade
by_grade <- sleep_tidy %>%
            nest(-Grade)

#Model comparison (total number of sleep hours as a covariate and moderator)
sleep_models <- by_grade %>%
                mutate(m1 = map(data, ~lm(Depression ~ Insomnia, data = .x)),
                       m2 = map(data, ~lm(Depression ~ Insomnia + Sleep_Hours, data = .x)),
                       comp12 = map2(m1, m2, anova),
                       p12 = map_dbl(comp12, list("Pr(>F)", 2)))

#Extracing the r^2 values by model across grade
sleep_models2 <- sleep_models %>% 
                 gather(model, output, m1:m2) %>%
                 mutate(r2 = map_dbl(output, ~summary(.x)$r.squared))
```

Plot 1
===================================== 

### National Longitudinal Study of Adolescent to Adult Health

```{r Plot 1}
#Version 3 - Common breakfast food choices by grade
bfast_count %>% 
            gather(food, count) %>% 
            ggplot(aes(reorder(food, count), count)) +
            geom_bar(aes(fill = food), stat="identity") + 
            coord_flip() +
            scale_fill_viridis_d(option="magma") +
            theme_minimal() +
            labs(title = "Common Breakfast Food Choices",
                 subtitle = "For 7th-12th Graders",
                 caption = "Data Collected 1994-1995",
                 x = "",
                 y = "Count") +
            theme (legend.position = "none")
```

> What are the most popular breakfast items for 7th-12th Graders?  Participants were asked to indicate all of the breakfast items that they consume on a regular basis. Unsurprisingly, both milk and cereal were the most commonly chosen answers while coffee, tea, and snack foods were the least commonly consumed.

Plot 2
===================================== 

### National Longitudinal Study of Adolescent to Adult Health

```{r Plot 2}
#Version 3 - Average Weekly Screen Time across grade, faceted by racial identity
p <- screen_7 %>% 
     group_by(Grade, race) %>% 
     summarize(mean_screen = mean(screen_time)) %>%
     ungroup() %>% 
     group_by(race) %>% 
     nest() %>% 
     mutate(plot = map2(data, race, ~
     ggplot(.x, aes(reorder(Grade, desc(Grade)), mean_screen)) +
     geom_col(aes(fill = Grade)) + 
     coord_flip() +
     scale_fill_viridis_d() +
     theme_minimal() +
     labs(title = "Average Weekly Screen Time",
          subtitle = glue("{.y}"),
          caption = "Data Collected 1994-1995",
          x = "Grade",
          y = "Average Weekly Screen Time (in minutes)") +
     theme(legend.position = "none",
           plot.title = element_text(size = 8),
           plot.subtitle = element_text(size = 7),
           plot.caption = element_text(size = 5),
           axis.title = element_text(size = 6))))

#Defining plots
p1 <- p$plot[[1]]
p2 <- p$plot[[2]]
p3 <- p$plot[[3]]
p4 <- p$plot[[4]]
p5 <- p$plot[[5]]

#Plot grid
require(cowplot)
theme_set(theme_cowplot(font_size = 12))
plot_grid(p1, p2, p3, p4, p5)
```

> What is the average screen time by grade iterated across race?  Participants were asked to indicate separately how many minutes per week they watched television, videos, and played videogames. We created a composite measure for general weekly screen time and found the average for each grade and dominant race category. From this we can see that for White participants, screen time gernerally decreases as grade increases. However, this pattern was not consistent for other race categories and screen time remained fairly consistent across grades for Black and African American participants. 

Plot 3
===================================== 

### National Longitudinal Study of Adolescent to Adult Health


```{r Plot 3}
#Version 3 - R^2 values of model comparison for insomnia predicting depression across grade
sleep_models2 %>% 
              mutate(fct_relevel(Grade, "Grade 7", "Grade 8", "Grade 9", "Grade 10", "Grade 11", "Grade 12")) %>% 
              ggplot(aes(model, r2)) +
                  geom_col(aes(fill = model)) +
                  facet_wrap(~Grade) +
                  scale_fill_OkabeIto() +
                  labs(title = "Insomnia (Model 1) vs. Insomnia and Total Sleep Time (Model 2) Predicting Depression",
                       caption = "Data Collected 1994-1995",
                       x = "Model",
                       y = "R^2") +
                  guides(fill = "none") +
                  theme(legend.position = "none",
                        plot.title = element_text(size = 9))
```

> Description of plot
